HPC--101\\Onboarding

### 2016-01-22 hpc_101/paper.tex
Fixed some spelling

\subsection{{\craycs}}
\begin{frame}
\frametitle{{\craycs} -- History}
\begin{itemize}
 \item Initial investment of 1.8 Million by the University of {\hawaii} (UH)
 \item Deilvered in October of 2014
 \item Accepted in December of 2014 
 \item Early adopter testing started in January 2015
 \item Opened for general use in April 2015
 \item As of October 2015, more than 200 users have been granted access to the cluster
\end{itemize}
\end{frame}

@@

\begin{frame}
	\frametitle{Overview -- Cluster Interaction}
	\begin{itemize}
		\item{Connecting to a cluster @ UH}
			\begin{itemize}
			\item Login to the cluster
			\item Verify user permissions
			\end{itemize}
    {\semitransp[25]{\item User directories
		\item Transferring files
		\begin{itemize}{\semitransp[25]{
			\item Globus
		}}\end{itemize}
		\item Software
		\begin{itemize}{\semitransp[25]{
			\item Modules
			\item Acquiring software
			\item Compiliers
			}}
		\end{itemize}
		\item Managing user jobs
		\begin{itemize}{\semitransp[25]{
			\item Job scheduler
			\item Using SLURM
			\item Partitions			
			\item Submitting jobs (Examples)
			}}
		\end{itemize}			
		}}
	\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Partition Details}
\resizebox{0.95\textwidth}{!}{%
\begin{tabular}{l || c || c || c || c || c || c}
\toprule                                                                    
\textbf{Partition} & \textbf{Time} & \textbf{Nodes per job} & \textbf{Priority} & \textbf{Shared} & \textbf{Preempt Mode} & \textbf{Memory per CPU (MB)} \\
%\toprule                                                                    
%\toprule                                                                    
\midrule
\midrule
community.q & \begin{tabular}{l r} \textbf{Default} & 0-00:10:00~\\ \textbf{Max} & 3-00:00:00\end{tabular} & \begin{tabular}{c c} \textbf{Min} & \padfrom{\ \ \ }{1}~\\ \textbf{Max} & \padfrom{\ \ \ }{20}\end{tabular} & 10 & NO & OFF & \begin{tabular}{l c}\textbf{Default} & \padfrom{\ \ \ \ \ \ \ }{3250}~\\ \textbf{Max} & \padfrom{\ \ \ \ \ \ \ }{6500}\end{tabular}\\
\hline
exclusive.q & \begin{tabular}{l r}\textbf{Default} & 0-00:10:00~\\ \textbf{Max} & 3-00:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min}& \padfrom{\ \ \ }{1}~\\ \textbf{Max}&\padfrom{\ \ \ }{20}\end{tabular} & 10 & EXCLUSIVE & OFF & \begin{tabular}{l c}\textbf{Default} & \padfrom{\ \ \ \ \ \ \ \ \ }{$\infty$}~\\ \textbf{Max} & \padfrom{\ \ \ \ \ \ \ }{6500}\end{tabular}\\
\hline
kill.q & \begin{tabular}{l r}\textbf{Default} & 0-00:10:00~\\ \textbf{Max} & 3-00:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min} & \padfrom{\ \ \ }{1}~\\ \textbf{Max} &\padfrom{\ \ \ }{12}\end{tabular} & 10 & NO & REQUEUE & \begin{tabular}{l c}\textbf{Default} & \padfrom{\ \ \ \ \ \ \ }{3250}~\\ \textbf{Max} & \padfrom{\ \ \ \ \ \ \ }{6500}\end{tabular}\\
\hline
htc.q & \begin{tabular}{l r}\textbf{Default} & 0-00:10:00~\\ \textbf{Max} & 3-00:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min} & \padfrom{\ \ \ }{1}~\\ \textbf{Max} &\padfrom{\ \ \ }{1}\end{tabular} & 1 & NO & REQUEUE & \begin{tabular}{l c}\textbf{Default} & \padfrom{\ \ \ \ \ \ \ }{3250}~\\ \textbf{Max} & \padfrom{\ \ \ \ \ \ \ }{6500}\end{tabular}\\
\hline
lm.q & \begin{tabular}{l r}\textbf{Default} & 0-00:10:00~\\ \textbf{Max} & 3-00:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min} & \padfrom{\ \ \ }{1}~\\ \textbf{Max} &\padfrom{\ \ \ }{1}\end{tabular} & 10 & NO & OFF & \begin{tabular}{l c}\textbf{Default} & \padfrom{\ \ \ \ \ \ \ \ \ }{$\infty$}~\\ \textbf{Max} & \padfrom{\ \ \ \ \ \ }{262100}\end{tabular}\\
\hline
sb.q & \begin{tabular}{l r}\textbf{Default} & 0-00:05:00~\\ \textbf{Max} & 0-01:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min} & \padfrom{\ \ \ }{1}~\\ \textbf{Max} &\padfrom{\ \ \ }{2}\end{tabular} & 10 & NO & OFF & \begin{tabular}{l c}\textbf{Default} & \padfrom{\ \ \ \ \ \ \ }{3250}~\\ \textbf{Max} & \padfrom{\ \ \ \ \ \ \ }{6500}\end{tabular}\\
\bottomrule 
\end{tabular}   
}
\\
\bigskip
Partition details also available on the \href{http://www.hawaii.edu/its/ci/hpc-resources/slurm-partitions/}{{\ci} website} or by using the following command:
\\
\texttt{$[$login \ctilde$]$\$ scontrol show partition $<$partition name$>$}
\end{frame}

\subsection{Interactive Job -- srun}
\frametitle{SLURM Job Scripts}
\begin{frame}
\frametitle{Interactive Job with SLURM}
	\begin{block}{Interactive session (no X11)}\tiny
	$[$login \ctilde$]$\$ srun \ddash{}immediate \ddash{}partition sb.q \ddash{}nodes 1 \ddash{}cpus-per-task 5 \ddash{}tasks-per-node 1 \ddash{}time 0-01:00 \ddash{}pty /bin/bash
	\end{block}

	\begin{block}{Interactive session (with X11)}\tiny
		\begin{enumerate}
			\item Connect via SSH using the -Y option, X11 forwarding enabled
			\item run srun.x11 to start a session on a node
		\end{enumerate}
		~\\
		~\\
		$[$local \ctilde$]$\$ ssh -Y user99@uhhpc1.its.hawaii.edu	~\\
		$[$login \ctilde$]$\$ srun.x11 \ddash{}immediate \ddash{}partition sb.q \ddash{}nodes 1 \ddash{}cpus-per-task 5 \ddash{}tasks-per-node 1 \ddash{}time 0-01:00	~\\
		$[$compute-0001 \ctilde$]$\$ xterm	~\\
	\end{block}
\end{frame}

@@

\subsection{Login Node Usage Policy}
\begin{frame}
\frametitle{Login Node Usage Policy}\footnotesize
The login nodes are a shared resource and are the only access to the cluster for hundreds of user and are meant to provide the following functionality for all users: 
\begin{itemize}
\item Providing ssh shell access 
\item Facilitate the transfer files to and from the cluster:\\Globus, sftp, scp, rsync
\item Launching and monitoring SLURM jobs (batch and interactive)
\item Modifying text files with a text editor: vi/vim, emacs, nano
\end{itemize}
\bigskip
\begin{itemize}
\item[--] If we identify or are notified that a user is running computation on the login nodes, the application will be killed
\item[--] If we determine that a user repeatly violates the login node policy, even after being warned, the repeat offender can have their cluster account disabled
\end{itemize}
\btVFill
\begin{center}
\footnotesize \textbf{\emph{Login node usage policy is subject to change~\\Users will be notified via email prior to changes taking effect}}
\end{center}
\end{frame}

>>>>

\subsection{{\craycs}}
\begin{frame}
\frametitle{{\craycs} -- History}
\begin{itemize}
 \item Initial investment of 1.8 Million by the University of {\hawaii} (UH)
 \item Delivered in October of 2014
 \item Accepted in December of 2014 
 \item Early adopter testing started in January 2015
 \item Opened for general use in April 2015
 \item As of October 2015, more than 200 users have been granted access to the cluster
\end{itemize}
\end{frame}

@@

\begin{frame}
	\frametitle{Overview -- Cluster Interaction}
	\begin{itemize}
		\item{Connecting to a cluster @ UH}
			\begin{itemize}
			\item Login to the cluster
			\item Verify user permissions
			\end{itemize}
    {\semitransp[25]{\item User directories
		\item Transferring files
		\begin{itemize}{\semitransp[25]{
			\item Globus
		}}\end{itemize}
		\item Software
		\begin{itemize}{\semitransp[25]{
			\item Modules
			\item Acquiring software
			\item Compilers
			}}
		\end{itemize}
		\item Managing user jobs
		\begin{itemize}{\semitransp[25]{
			\item Job scheduler
			\item Using SLURM
			\item Partitions			
			\item Submitting jobs (Examples)
			}}
		\end{itemize}			
		}}
	\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Partition Details}
\resizebox{0.95\textwidth}{!}{%
\begin{tabular}{l || c || c || c || c || c || c}
\toprule                                                                    
\textbf{Partition} & \textbf{Time} & \textbf{Nodes per job} & \textbf{Priority} & \textbf{Shared} & \textbf{Preempt Mode} & \textbf{Memory per CPU (MB)} \\
%\toprule                                                                    
%\toprule                                                                    
\midrule
\midrule
community.q & \begin{tabular}{l r} \textbf{Default:} & 0-00:10:00~\\ \textbf{Max:} & 3-00:00:00\end{tabular} & \begin{tabular}{c c} \textbf{Min:} & \padfrom{\ \ \ }{1}~\\ \textbf{Max:} & \padfrom{\ \ \ }{20}\end{tabular} & 10 & NO & OFF & \begin{tabular}{l c}\textbf{Default:} & \padfrom{\ \ \ \ \ \ \ }{3250}~\\ \textbf{Max:} & \padfrom{\ \ \ \ \ \ \ }{6500}\end{tabular}\\
\hline
\hline
exclusive.q & \begin{tabular}{l r}\textbf{Default:} & 0-00:10:00~\\ \textbf{Max:} & 3-00:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min:}& \padfrom{\ \ \ }{1}~\\ \textbf{Max:}&\padfrom{\ \ \ }{20}\end{tabular} & 10 & EXCLUSIVE & OFF & \begin{tabular}{l c}\textbf{Default:} & \padfrom{\ \ \ \ \ \ \ \ \ }{$\infty$}~\\ \textbf{Max:} & \padfrom{\ \ \ \ \ \ \ }{6500}\end{tabular}\\
\hline
\hline
kill.q & \begin{tabular}{l r}\textbf{Default:} & 0-00:10:00~\\ \textbf{Max:} & 3-00:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min:} & \padfrom{\ \ \ }{1}~\\ \textbf{Max:} &\padfrom{\ \ \ }{12}\end{tabular} & 10 & NO & REQUEUE & \begin{tabular}{l c}\textbf{Default:} & \padfrom{\ \ \ \ \ \ \ }{3250}~\\ \textbf{Max:} & \padfrom{\ \ \ \ \ \ \ }{6500}\end{tabular}\\
\hline
\hline
htc.q & \begin{tabular}{l r}\textbf{Default:} & 0-00:10:00~\\ \textbf{Max:} & 3-00:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min:} & \padfrom{\ \ \ }{1}~\\ \textbf{Max:} &\padfrom{\ \ \ }{1}\end{tabular} & 1 & NO & REQUEUE & \begin{tabular}{l c}\textbf{Default:} & \padfrom{\ \ \ \ \ \ \ }{3250}~\\ \textbf{Max:} & \padfrom{\ \ \ \ \ \ \ }{6500}\end{tabular}\\
\hline
\hline
lm.q & \begin{tabular}{l r}\textbf{Default:} & 0-00:10:00~\\ \textbf{Max:} & 3-00:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min:} & \padfrom{\ \ \ }{1}~\\ \textbf{Max:} &\padfrom{\ \ \ }{1}\end{tabular} & 10 & NO & OFF & \begin{tabular}{l c}\textbf{Default:} & \padfrom{\ \ \ \ \ \ \ \ \ }{$\infty$}~\\ \textbf{Max:} & \padfrom{\ \ \ \ \ \ }{262100}\end{tabular}\\
\hline
\hline
sb.q & \begin{tabular}{l r}\textbf{Default:} & 0-00:05:00~\\ \textbf{Max:} & 0-01:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min:} & \padfrom{\ \ \ }{1}~\\ \textbf{Max:} &\padfrom{\ \ \ }{2}\end{tabular} & 10 & NO & OFF & \begin{tabular}{l c}\textbf{Default:} & \padfrom{\ \ \ \ \ \ \ }{3250}~\\ \textbf{Max:} & \padfrom{\ \ \ \ \ \ \ }{6500}\end{tabular}\\
\bottomrule 
\end{tabular}   
}
\\
\bigskip
Partition details also available on the \href{http://www.hawaii.edu/its/ci/hpc-resources/slurm-partitions/}{{\ci} website} or by using the following command:
\\
\texttt{$[$login \ctilde$]$\$ scontrol show partition $<$partition name$>$}
\end{frame}

\subsection{Interactive Job -- srun}
\frametitle{SLURM Job Scripts}
\begin{frame}
\frametitle{Interactive Job with SLURM}
	\begin{block}{Interactive session (no X11)}\tiny
	$[$login \ctilde$]$\$ srun \ddash{}immediate \ddash{}partition sb.q \ddash{}nodes 1 \ddash{}cpus-per-task 5 \ddash{}tasks-per-node 1 \ddash{}time 0-01:00:00 \ddash{}pty /bin/bash
	\end{block}

	\begin{block}{Interactive session (with X11)}\tiny
		\begin{enumerate}
			\item Connect via SSH using the -Y option, X11 forwarding enabled
			\item run srun.x11 to start a session on a node
		\end{enumerate}
		~\\
		~\\
		$[$local \ctilde$]$\$ ssh -Y user99@uhhpc1.its.hawaii.edu	~\\
		$[$login \ctilde$]$\$ srun.x11 \ddash{}immediate \ddash{}partition sb.q \ddash{}nodes 1 \ddash{}cpus-per-task 5 \ddash{}tasks-per-node 1 \ddash{}time 0-01:00:00	~\\
		$[$compute-0001 \ctilde$]$\$ xterm	~\\
	\end{block}
\end{frame}

@@

\subsection{Login Node Usage Policy}
\begin{frame}
\frametitle{Login Node Usage Policy}\footnotesize
The login nodes are a shared resource and are the only access to the cluster for hundreds of user and are meant to provide the following functionality for all users: 
\begin{itemize}
\item Providing ssh shell access 
\item Facilitate the transfer files to and from the cluster:\\Globus, sftp, scp, rsync
\item Launching and monitoring SLURM jobs (batch and interactive)
\item Modifying text files with a text editor: vi/vim, emacs, nano
\end{itemize}
\bigskip
\begin{itemize}
\item[--] If we identify or are notified that a user is running computation on the login nodes, the application will be killed
\item[--] If we determine that a user repeatedly violates the login node policy, even after being warned, the repeat offender can have their cluster account disabled
\end{itemize}
\btVFill
\begin{center}
\footnotesize \textbf{\emph{Login node usage policy is subject to change~\\Users will be notified via email prior to changes taking effect}}
\end{center}
\end{frame}
